Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-16 doc/PRF2022/PRF_main.tex
update

\begin{abstract}
% insert abstract here

{\bf To do list:}

Unbouned Flow: 
\begin{enumerate}
\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).

\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
Add energy profiles to check local/absolute minimum. Superimpose these
    energies on Figure 3, but scale the energies by the number of Janus
    particles so that it is ``energy per particle"

\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.

\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.

\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
\end{enumerate}

{\bf May do list:}
Channel Flow: 
\begin{enumerate}
\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.

\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.

\end{enumerate}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 60 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$.}
\end{caption}
\end{figure}

@@

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.24\textwidth]{shear_0.png}
  \includegraphics[width=0.24\textwidth]{shear_1000.png}
  \includegraphics[width=0.24\textwidth]{shear_2000.png} 
  \includegraphics[width=0.24\textwidth]{shear_2000.png} \\
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

>>>>

\begin{abstract}
% insert abstract here
%
%{\bf To do list:}
%
%Unbouned Flow: 
%\begin{enumerate}
%\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
%  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
%    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).
%
%\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
%Add energy profiles to check local/absolute minimum. Superimpose these
%    energies on Figure 3, but scale the energies by the number of Janus
%    particles so that it is ``energy per particle"
%
%\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
%Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details. 
%
%\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.
%
%\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
%\end{enumerate}
%
%
%{\bf May do list:}
%Channel Flow: 
%\begin{enumerate}
%\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.
%
%\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.
%
%\end{enumerate}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 198 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$. (b)-(d) show the equilibrium states for $b=1, 2, 0$, respectively.}
\end{caption}
\end{figure}

@@

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{shear_0.png}
  \includegraphics[width=0.32\textwidth]{shear_1000.png}
  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}
